A Generalized Reduced Linear Program for Markov Decision Processes

### 2016-07-08 single/polbnd.tex
Chandru's shortened version

\section{Error Analysis}\label{sec:errana}
We now define the two projection operators which are central to our error analysis. The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined below, see \eqref{gamdef}.
\begin{definition}\label{lubpop}
Given $J\in \R^n$ and the nonnegative valued vector $c\in \R^n_+$, define $r_{c,J}$ to be the solution to 
\label{lubplp}
\begin{split}
 \underset{r\in \N'}{\min} &\,\, c^\top \Phi r\,,\\
 \text{s.t.}& \mb \Phi r\geq  TJ.
 \end{split}
Then, for $J\in \R^n$, $\Gamma J$,
the least upper bound projection of $J$ is defined as 
\begin{align}\label{gamdef}
(\Gamma J)(i)\eqdef(\Phi r_{e_i,J})(i),\quad i=1,\ldots,n\,.
\end{definition}
\begin{remark}\label{ubrem}
To understand the meaning of $\Gamma$ (and $\hg$) define 
\begin{align}\label{ubclass}
\F_J\eqdef\{\,\Phi r\,:\,\Phi r\geq TJ, r\in \N\,\},
where $J\in \R^n$. Thus $\F_J$ contains vectors in the span of $\Phi$ that upper bound $TJ$. Further, since $(\Gamma J)(i) = \min\{ V(i) \,:\, V\in \F_J \}$, it also follows that $ V\ge \Gamma J $ holds for any $V\in \F_J$.
\end{remark}
The approximate least upper bound (ALUB) projection operator $\hg \colon \R^n \ra \R^n$ is defined as below:
\begin{definition}\label{alubpop}
Given $J\in \R^n$ and the nonnegative valued vector $c\in \R^n_+$, define $r'_{c,J}$ to be the solution to 
\begin{align}\label{alubplp}
 \underset{r\in \N'}{\min}& \,\mb c^\top \Phi r\,,\nn\\
 \text{s.t.}& \,\,\, W^\top E \Phi r\geq W^\top HJ.
Further, define $\hg J$  as 
\begin{align}\label{tgamdef}
(\hg J)(i)\eqdef(\Phi r'_{e_i,J})(i), \mb i=1,\ldots,n\,.
\end{definition}
\begin{lemma}\label{lpsol}
Let $A\in \R^{u\times v}$, $b,c\in \R^u$ and $b_0=Ax_0$ for 
some $x_0 \in \R^v$, $\N' \subset \R^v$ such that $\N' =x_0+ \N'$. Then
&\min\{c^\top Ax:Ax\geq b+b_0, x\in \N'\} \nn\\
&=\min\{c^\top A y:Ay \geq b, y \in \N' \}+c^\top b_0.
\end{lemma}
The claim follows by the change of variables $y := x-x_0$.
\noindent 
%Note that under our assumptions on $\N$, $\hg$ is well-defined.
%\begin{align*}
%r^*\eqdef\argmin_{r\in R^k}||J^*-\Phi r||_{\mn}\,.
%\end{align*}
%where $\psi$ is a Lyapunov function as in \cref{lyap}.
\begin{lemma}\label{bestbndmn}
We have
||J^*-\Gamma J^*||_{\mn}\leq 2||J^*-\Phi r^*||_{\mn}.
\end{lemma}
Define $\eps = \norm{J^* - \Phi r^*}_{\mn}$ so that
$ J^*-\Phi r^* \le \eps \psi$ and $\Phi r^* - J^*\le \eps \psi$. Then from \cref{grlpassmp}-\eqref{ass:n4} it follows that $\Phi( r^* + \eps r_0 ) = \Phi r^* + \eps \psi \ge J^* = T J^*$. From the definition of $\Gamma$ in \eqref{gamdef} and \cref{ubrem}, we know that $\Phi r^*+\eps \psi \geq \Gamma J^*\geq J^*$. The result follows by noting that $2\eps\psi\geq \Phi r^*+\eps\psi -J^*\geq \Gamma J^*-J^*\geq 0$.
\begin{lemma}\label{tgmonotone}
For $J_1, J_2\in \R^n$ such that $J_1\leq J_2$, we have $\hg J_1\leq \hg J_2$.
\end{lemma}
Given $J\in \R^n$, let $\F_J\eqdef\{\,\Phi r\,: W^\top E \Phi r\geq W^\top HJ, r\in \N'\,\}\,$. Choose any $i\in \{1, \ldots, n\}$. Since $J_1\leq J_2$, from \cref{monotone} and \cref{grlpassmp}-\eqref{wassump} it follows that $W^\top H J_1\leq W^\top H J_2$. Hence, $\F_{J_2} \subset \F_{J_1}$ and thus $(\hg J_1)(i) \le (\hg J_2)(i)$.  Since $i$ was arbitrary, the result follows. 
\begin{lemma}\label{maxnormmn}
Assume that $\hg: \R^n \to \R^n$ is monotone and 
that there exists some $\beta\in [0,1)$ such that for any $J\in \R^n$ and $t>0$,
\label{eq:shiftmn}
\hg( J + t \psi) \le \hg J + \beta t \psi,
for any $J\in \R^n$ and $t\ge 0$.
Then $\hg$ is a $\norm{\cdot}_{\mn}$ contraction with factor $\beta$.
\end{lemma}
First, we show that for any $t\ge 0$,  $J\in \R^n$,
$\hg( J - t \psi) \ge \hg J - \beta t \psi$ also holds.
To see this define $J' = J-t\psi$. Then, $J = J'+t\psi$, hence $\hg J \le \hg J' + \beta t \psi$. Reordering this inequality gives the result.
Let $\eps = \norm{J_1 - J_2}_{\mn}$, where $J_1,J_2\in \R^n$ are arbitrary.
Then $J_2 - \eps \psi \le J_1 \le J_2 + \eps \psi$. 
By the monotonicity of $\hg$,
$\hg(J_2 - \eps \psi) \le \hg J_1 \le \hg(J_2 + \eps \psi)$. 
Using~\eqref{eq:shiftmn}, we get 
$\hg J_2 - \beta \eps \psi \le \hg J_1 \le \hg J_2 + \beta \eps \psi$, i.e., $-\beta \eps \psi \le \hg J_1 - \hg J_2 \le \beta \eps \psi$, from which the result follows.
\begin{corollary}\label{tmaxnormmn}
$T$ is a $\norm{\cdot}_{\mn}$-contraction with factor $\beta_{\psi}$.
\end{corollary}
%Returning to $\hg$, since we already now that $\hg$ is monotone (cf. \cref{gmonotone}), it remains to see that it satisfies \eqref{eq:shiftmn}:
\begin{lemma}\label{gshiftmn}
The operator $\hg$ satisfies \eqref{eq:shiftmn} with $\beta = \beta_\psi$.
%For any $J\in \R^n$, $t\in \R_+$, $\Gamma (J+ t \psi ) \le \Gamma J + \beta_{\psi} t \psi$.
\end{lemma}
By definition, for $1\le i \le n$, $(\hg (J+t\psi) )(i) = \min\{ e_i^\top \Phi r \,:\, W^\top E\Phi r \ge W^\top H(J+t\psi), r\in \N' \}$.
By \eqref{eq:psilin}, as $t>0$, $H(J+t\psi) \le HJ + t \beta_\psi \psi$ and hence $W^\top H(J+t\psi) \le W^\top (HJ + t \beta_\psi \psi)$. Thus,
$(\hg (J+t\psi) )(i) \le 
 \min\{ e_i^\top \Phi r \,:\, W^\top E\Phi r \ge W^\top HJ+t\beta_\psi \psi), r\in \N' \}$.
Now, using Lemma~\ref{lpsol} with $A=W^\top E \Phi$, $b=W^\top HJ$, $c=e_i$, $b_0=t\beta_\psi \psi$ 
and $x_0=t \beta_\psi r_0$, the statement follows since $A x_0 = b_0$ (from \cref{grlpassmp}-\eqref{lyap}) and $\N' = \N' + \alpha t r_0$ (from \cref{grlpassmp}-\eqref{ass:n4}).
%The result follows in a similar manner as the proofs for Lemmas~\ref{gshift} and ~\ref{tgshift} by using the result in Lemma~\ref{lpsol}.
%From this result and \cref{maxnormmn}, we immediately get that $\Gamma$ is a contraction in $\norm{\cdot}_{\mn}$:
\begin{comment}
\begin{theorem}\label{gmaxcontramn}
The operator $\Gamma  \colon \R^n\ra \R^n$ is a contraction operator in $\norm{\cdot}_{\mn}$ with factor $\beta_{\psi}$.
\end{comment}
%In a similar way, one can also show that $\hg$ is also a contraction:
\begin{theorem}\label{hgmaxcontramn}
The operator $\hg:\R^n\to\R^n$  is a contraction operator in $\norm{\cdot}_{\mn}$ with factor $\beta_{\psi}$.
%$\hg$ is also a contraction map in the weighted $L_\infty$ norm.
Follows from \cref{maxnormmn} and \cref{gshiftmn}.
\begin{comment}
We already know that $\hg$ is monotone. That $\hg$ satisfies~\cref{eq:shiftmn}
with $\beta = \beta_{\psi}$ follows similarly to the argument used in  \cref{tgshift}
with modifications similar to those introduced in the proof of \cref{gshiftmn}.
Then, \cref{gmaxcontramn} gives the desired result.
\end{comment}
In what follows we denote by $\hv$ the unique fixed point of $\hg$ i.e., $\hv = \hg \hv\,$. 
We now show that the vector $\hj$ dominates the vector $\hv$:
\begin{lemma}\label{relation1}
The vectors $\hv,\hj$ obey $\hj\geq\hv$.
\end{lemma}
Let $ r_1,  r_2,\ldots, r_n$ be solutions to the GRLP in \eqref{grlp} for $c=e_1, e_2,\ldots,e_n$, respectively,
and define $V_0\in \R^n$ by $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$, $1\le i \le n$.

It suffices to show that $V_1\eqdef \hg V_0 \le V_0 \le \hj$ since then the desired result follows
by defining $V_{n+1} = \hg V_n$, $n\ge 1$, noting that by \cref{tgmonotone}, $V_{n+1}\le V_{n}$ and by  \cref{tmaxnormmn}, $V_n \to \hv$.

Since $(\Phi r_j)(i) \ge (\Phi r_i)(i)$ also holds for any $1\leq i,j\leq n$ we have $V_0(i)  = (\Phi r_i)(i)$. Also, since $\hj(i) \ge (\Phi r_i)(i),1\leq i \leq n$ it follows that $\hj\geq V_0$. 
Now,  fix any $i$. 
We need to show that $V_1(i)=(\hg V_0)(i) = (\Phi r'_{e_i,V_0})(i) \leq V_0(i)$. 
By the definition of $r'_{e_i,V_0}$ we know that $(\Phi r'_{e_i,V_0})(i) \le (\Phi r)(i)$
holds for any $r\in \N$ such that $W^\top E \Phi r \ge W^\top H V_0$. 
Now it suffices to show that $r_i$ satisfies $W^\top E \Phi r_i \ge W^\top H V_0$. 
By definition, $r_i$ satisfies $W^\top E \Phi r_i \ge W^\top H \Phi r_i$.
Hence, by the monotone property of $H$ and \cref{grlpassmp}-\eqref{wassump} it is sufficient if $\Phi r_i \ge V_0$.
This however directly follows from the definition of $V_0$.
\begin{lemma}\label{relation2}
The vectors $\hv,\tj$ obey $\tj\geq\hv$.
\end{lemma}
%The proof follows in a similar manner as the proof of \Cref{relation1}. To elaborate, 
Let $ r_1,  r_2,\ldots, r_n$ be solutions to the ALP in \eqref{alp} (with an additional constraint that the solution be restricted to $\N$) for $c=e_1, e_2,\ldots,e_n$, respectively,
and define $V_0\in \R^n$ by $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$, $1\le i \le n$. The rest of the proof 
follows in the same manner as the proof of \cref{relation1}.
\begin{lemma}\label{srw}
A vector
$\hat{r} \in \R^k$ is a solution to GRLP \eqref{grlp} iff it solves the following program:
\begin{align}\label{grlpeqprog}
\begin{split}
\min_{r\in \N}\, &||\Phi r-\hv||_{1,c}\\
\text{s.t.}\mb &\, W^\top E \Phi r\geq W^\top H \Phi r.
\end{split}
\end{lemma}
We know from Lemma~\ref{relation2} that $\hj = \Phi \hr \geq\hv$, and thus
the solutions to \eqref{grlp} do not change if we add the constraint $\Phi r \ge \hv$.
Now, under this constraint, minimizing $c^\top \Phi r$ is the same as minimizing 
||\Phi r-\hv||_{1,c}=\sum_{i=1}^n c(i) |(\Phi r)(i)-\hv(i)|=c^\top \Phi r-c^\top \hv\,.
\begin{lemma}\label{srwalp}
A vector
$\tr \in \R^k$ is a solution to ALP \eqref{alp} iff it solves the following program:
\begin{align}\label{grlpeqprog}
\begin{split}
\min_{r\in \R^k}\, &||\Phi r-\hv||_{1,c}\\
\text{s.t.}\mb &\, \Phi r\geq  T \Phi r.
\end{split}
\end{lemma}
We know from Lemma~\ref{relation2} that $\tj = \Phi \tr \geq\hv$, and the rest of the arguments follow in the same manner as proof for \cref{srw}.
\begin{lemma}\label{cmt1mn}
We have
||J^*-\hv||_{\mn}&\leq \frac{1}{{1-\beta_{\psi}}}\big(2||J^*-\Phi r^*||_{\mn}&\nn\\+||\Gamma J^*-\hg J^*||_{\mn}\big).
\end{lemma}
Recall that $\hg \hv=\hv$. By the triangle inequality,
&||J^*-\hv||_\mn\\&\leq ||J^*-\hg J^*||_\mn+||\hg J^*-\hg \hv||_\mn\\&\leq ||J^*-\hg J^*||_\mn+\beta_\psi || J^*- \hv||_\mn,
and so by reordering and with another triangle inequality,
\begin{align}\label{jhv}
&\norm{J^*-\hv}_{\mn} \nn\\&\le \frac{\norm{ J^*-\hg J^*}_{\mn}}{1-\beta_\psi}\nn\\
&\le \frac{\norm{ J^*-\Gamma J^*}_{\mn}+\norm{\Gamma J^* - \hg J^*}_{\mn}}{1-\beta_\psi}\,.
The proof follows by applying \cref{bestbndmn} on \eqref{jhv}.
We now recall Lemma~$5$ from Section 4.2 of \cite{ALP}. 
For this result, recall that $r_0 \in \R^k$ is the vector such that $\psi = \Phi r_0$ by assumption.
\begin{lemma}\label{restate}
%Let $\psi$ be a Lyapunov function that belongs to the column span of $\Phi$ ,
For  $r \in \R^k$ arbitrary vector, let $r'$ be
 r'= r+||J^*-\Phi r||_{\mn} \left(\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\right)\, r_0.
Then $r'$ is feasible for the ALP in \eqref{alp}.
\end{lemma}
Recall that $\hv$ is the fixed point of $\hg$ and $\hj=\Phi \hr$ is the solution to the GRLP
\eqref{grlp}. 
\begin{theorem}\label{mt2mn}
We have
||\hj-\hv||_{1,c}&\leq \frac{c^\top \psi}{1-\beta_\psi}(4||J^*-\Phi r^*||_{\mn}\nn\\
&+||\Gamma J^*-\hg J^*||_{\mn}).
Let $\gamma=||J^*-\Phi r^*||_{\mn}$. 
Then, by choosing $r'$ as in Lemma~\ref{restate} we have
\begin{align}\label{part}
&||\Phi r'-J^*||_{\mn}\nn\\&\leq ||\Phi r^*-J^*||_{\mn}+||\Phi r'-\Phi r^*||_{\mn}\nn\\
&=\gamma+\frac{1+\beta_\psi}{1-\beta_\psi}\gamma\nn\\
&=\frac{2}{1-\beta_\psi}\gamma.
%We know that $\tr \in \N$ by \cref{grlpassmp}-\eqref{nassmp} and 
$r'$ is feasible for the ALP in \eqref{grlp} by \cref{restate}. Then from \cref{srwalp} it follows that
%As a result, from \cref{srw} it follows that
&||\hj-\hv||_{1,c}\leq||\Phi \tr-\hv||_{1,c}\leq||\Phi r'-\hv||_{1,c}\nn\\
&=\sum_{s\in S}c(s)\psi(s)\frac{|\Phi r'(s)-\hv(s)|}{\psi(s)}\nn\\
&\leq c^\top \psi ||\Phi r'-\hv||_{\mn}\nn\\
&\leq c^\top \psi (||\Phi r'-J^*||_{\mn}+||J^*-\hv||_{\mn}).
The result follows from \cref{cmt1mn} and \eqref{part}.
%\textbf{Main Result~$1$: Prediction Error bound in weighted $L_\infty$-norm}
\begin{theorem}[Prediction error bound in $\norm{\cdot}_{\mn}$]
\label{cmt2mn}
%Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2mn}, then
It holds that
\begin{align}\label{finalbndmn}
||J^*-\hj||_{1,c}&\leq\frac{c^\top\psi}{1-\beta_\psi}(6 ||J^*-\Phi r^*||_{\mn}\nn\\
&+2||\Gamma J^*-\hg J^*||_{\mn}).
We have
&||J^*-\hj||_{1,c}\nn\\
&\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}\nn\\
&\leq c^\top \psi ||J^*-\hv||_{\mn}+||\hv-\hj||_{1,c}.\nn
The result now follows from Lemma~\ref{cmt1mn} and Theorem~\ref{mt2mn}.

@@

&||J_{\hu}-\hj||_{1,c}\nn\\&=||(I-\alpha P_{\hu})^{-1}(T\hj-\hj)||_{1,c}\nn\\

@@

vector whose $i$th component is $|(T\hj)(i) - \hj(i)|$. Further, the last inequality follows
since $T$ is a $\norm{\cdot}_{\mn}$ contraction with factor $\beta_{\psi}$ as noted earlier.

@@

\begin{comment}

@@

\end{comment}

>>>>

%\textbf{Main Result $2$: Control Error bound in modified $L_\infty$-norm}\\

@@

||J_{\hu}-\hj||_{1,c}&=||(I-\alpha P_{\hu})^{-1}(T\hj-\hj)||_{1,c}\nn\\

@@

vector whose $i$th component is $|(T\hj)(i) - \hj(i)|$ and the last inequality follows
since $T$ is a $\norm{\cdot}_{\mn}$ contraction with factor $\beta_{\psi}$, as we noted it earlier.

@@

%\begin{comment}

@@

%\end{comment}
%The following result (Theorem~\ref{st}) supports Claim~$1$ in the above.\\
The error term $\etmn$ gives new insights into constraint sampling. 
\begin{theorem}[ On Constraint Sampling]\label{st}
Let $s\in S$ be a state whose constraint was sampled. Then
\begin{align}\label{sampexp}
|\Gamma J^*(s)-\hg J^*(s)|<|\Gamma J^*(s)-J^*(s)|.
Let $r_{e_s}$ and $\hat{r}_{e_s}$ be solutions to the linear programs in \eqref{lubplp} and \eqref{alubplp} respectively for $c=e_s$ and $J=J^*$. It is easy to note that $r_{e_s}$ is feasible for the linear program in \eqref{alubplp} for $c=e_s$ and $J^*$, and hence it follows that $(\Phi r_{e_s})(s)\geq (\Phi \hat{r}_{e_s})(s)$. However, since all the constraints with respect to state $s$ have been sampled we know that $(\Phi \hat{r}_{e_s})(s)\geq J^*$. The proof follows from noting that $(\Gamma J^*)(s)=(\Phi r_{e_s})(s)$ and $\hg J^*(s)=(\Phi \hat{r}_{e_s})(s)$.

### 2016-07-08 single/strel.tex
Chandru's shortened version

%!TEX root =  autocontgrlp.tex
\section{A simple bound}
The following lemmas relate the fixed point $\hv$ of $\hg$ to the solution $\hj$ of the GRLP in \eqref{grlp}.
\begin{lemma}\label{srw}
A vector
$\hat{r} \in \R^k$ is a solution to GRLP \eqref{grlp} iff it solves the following program:
\begin{align}\label{grlpeqprog}
\begin{split}
\min_{r\in \R^k}\, &||\Phi r-\hv||_{1,c}\\
\text{s.t.}\mb &\, W^\top E \Phi r\geq W^\top H \Phi r\,, \qquad r\in \N\,.
\end{split}
\end{align}
\end{lemma}
\begin{proof}
We know from Lemma~\ref{relation2} that $\hj = \Phi \hr \geq\hv$, and thus
the solutions to \eqref{grlp} do not change if we add the constraint $\Phi r \ge \hv$.
Now, under this constraint, minimizing $c^\top \Phi r$ is the same as
 minimizing 
\begin{align*}
||\Phi r-\hv||_{1,c}=\sum_{i=1}^n c(i) |(\Phi r)(i)-\hv(i)|=c^\top \Phi r-c^\top \hv\,.
\end{align*} 
\end{proof}
\begin{theorem}\label{mt2}
%Let $\hv$ be the solution to the iterative scheme in \eqref{apvi} and let $\hj=\Phi \hr$ be the solution to the GRLP. Let $\bj$ be the best possible approximation to $J^*$ as in Definition~\ref{bestproj}, and $||\Gamma J^* -\hg J^*||_\infty$ be the error due to ALUB projection and let $r^*\eqdef\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_\infty$, then
It holds that
\begin{align}
||\hj-\hv||_{1,c}\leq\frac{4||J^*-\Phi r^*||_\infty+||\Gamma J^*-\hg J^*||_\infty}{1-\alpha}.
\end{align}
\end{theorem}
\begin{proof}
Let $\gamma=||J^*-\Phi r^*||_\infty$. Then, since $T$ is an $\alpha$-contraction in the $\max$-norm,
$||J^*-T\Phi r^*||_\infty=||TJ^*-T\Phi r^*||_\infty\leq\alpha\gamma$ and hence by the triangle inequality,
\begin{align}\label{eq:tphir}
||T\Phi r^*-\Phi r^*||_\infty&\leq(1+\alpha)\gamma\,.
\end{align}
Let $r'= r^*+t e_1$ with $t>0$ to be chosen later.
Then, from \cref{one},
$T\Phi r' = T(\Phi r^* + t \one) = T \Phi r^* + \alpha t \one \le \Phi r^* + (\alpha t+ (1+\alpha) \gamma) \one$,
 where the inequality follows from~\eqref{eq:tphir}.
 Choosing $t$ so that $t = \alpha t+ (1+\alpha) \gamma$, or $t = \frac{(1+\alpha)\gamma}{1-\alpha}$, we get
 that $T\Phi r' \le \Phi r'$. Hence, $r'$ is feasible to the ALP \eqref{alp} and 
since, thanks to \cref{wassump}, 
any feasible solution to \eqref{alp} is also a feasible solution to the GRLP  \eqref{grlp},
$r'$ is also feasible to \eqref{grlp}. Thus, 
\begin{align}
||\hj-\hv||_{1,c}&\leq||\Phi r'-\hv||_{1,c}\nn &(\text{thanks to Lemma~\ref{srw}}) \\ %\vspace{10pt}
&\leq||\Phi r'-\hv||_\infty\mb & (\text{since $c$ is a distribution})\nn\\
&\leq||\Phi r'-J^*||_\infty+||J^*-\hv||_\infty\,. & (\text{triangle inequality}) \label{mt2eq0}
\end{align}
Now, by another triangle inequality,
\begin{align}
||\Phi r'-J^*||_\infty&\leq ||\Phi r^* -J^*||_\infty+||\Phi r'-\Phi r^*||_\infty
\leq \gamma+\frac{(1+\alpha)\gamma}{1-\alpha}=\frac{2\gamma}{1-\alpha}.
\label{mt2eq1}
\end{align}
The result follows by combining this bound with \eqref{mt2eq0} and Corollary~\ref{cmt1}.
\end{proof}

\begin{corollary}[Prediction error bound]
\label{cmt2}
%Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2}, then \todoc{Where is the effect of $\chi$?}
We have
\begin{align}\label{finalbnd}
||J^*-\hj||_{1,c}\leq\frac{6 ||J^*-\Phi r^*||_\infty+2||\Gamma J^*-\hg J^*||_\infty}{1-\alpha}\,.
\end{align}
\end{corollary}
\begin{proof}
We have
$
||J^*-\hj||_{1,c}\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}
\leq||J^*-\hv||_\infty+||\hv-\hj||_{1,c}
$.
The result now follows from Corollary~\ref{cmt1} and Theorem~\ref{mt2}.
\end{proof}
The results presented in Corollary~\ref{cmt2} is in the $L_\infty$-norm. In the next section, we make use of Lyapunov functions to provide an improved bound in the weighted $L_\infty$-norm.

>>>>

%!TEX root =  autocontgrlp.tex
\section{A worst-case bound}
The following lemmas relate the fixed point $\hv$ of $\hg$ to the solution $\hj$ of the GRLP in \eqref{grlp}.
\begin{lemma}\label{srw}
A vector
$\hat{r} \in \R^k$ is a solution to GRLP \eqref{grlp} iff it solves the following program:
\begin{align}\label{grlpeqprog}
\begin{split}
\min_{r\in \R^k}\, &||\Phi r-\hv||_{1,c}\\
\text{s.t.}\mb &\, W^\top E \Phi r\geq W^\top H \Phi r\,, \qquad r\in \N\,.
\end{split}
\end{align}
\end{lemma}
\begin{proof}
We know from Lemma~\ref{relation2} that $\hj = \Phi \hr \geq\hv$, and thus
the solutions to \eqref{grlp} do not change if we add the constraint $\Phi r \ge \hv$.
Now, under this constraint, minimizing $c^\top \Phi r$ is the same as
 minimizing 
\begin{align*}
||\Phi r-\hv||_{1,c}=\sum_{i=1}^n c(i) |(\Phi r)(i)-\hv(i)|=c^\top \Phi r-c^\top \hv\,.
\end{align*} 
\end{proof}
\begin{theorem}\label{mt2}
%Let $\hv$ be the solution to the iterative scheme in \eqref{apvi} and let $\hj=\Phi \hr$ be the solution to the GRLP. Let $\bj$ be the best possible approximation to $J^*$ as in Definition~\ref{bestproj}, and $||\Gamma J^* -\hg J^*||_\infty$ be the error due to ALUB projection and let $r^*\eqdef\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_\infty$, then
It holds that
\begin{align}
||\hj-\hv||_{1,c}\leq\frac{4||J^*-\Phi r^*||_\infty+||\Gamma J^*-\hg J^*||_\infty}{1-\alpha}.
\end{align}
\end{theorem}
\begin{proof}
Let $\gamma=||J^*-\Phi r^*||_\infty$. Then, since $T$ is an $\alpha$-contraction in the $\max$-norm,
$||J^*-T\Phi r^*||_\infty=||TJ^*-T\Phi r^*||_\infty\leq\alpha\gamma$ and hence by the triangle inequality,
\begin{align}\label{eq:tphir}
||T\Phi r^*-\Phi r^*||_\infty&\leq(1+\alpha)\gamma\,.
\end{align}
Let $r'= r^*+t e_1$ with $t>0$ to be chosen later.
Then, from \cref{one},
$T\Phi r' = T(\Phi r^* + t \one) = T \Phi r^* + \alpha t \one \le \Phi r^* + (\alpha t+ (1+\alpha) \gamma) \one$,
 where the inequality follows from~\eqref{eq:tphir}.
 Choosing $t$ so that $t = \alpha t+ (1+\alpha) \gamma$, or $t = \frac{(1+\alpha)\gamma}{1-\alpha}$, we get
 that $T\Phi r' \le \Phi r'$. Hence, $r'$ is feasible to the ALP \eqref{alp} and 
since, thanks to \cref{wassump}, 
any feasible solution to \eqref{alp} is also a feasible solution to the GRLP  \eqref{grlp},
$r'$ is also feasible to \eqref{grlp}. Thus, 
\begin{align}
||\hj-\hv||_{1,c}&\leq||\Phi r'-\hv||_{1,c}\nn &(\text{thanks to Lemma~\ref{srw}}) \\ %\vspace{10pt}
&\leq||\Phi r'-\hv||_\infty\mb & (\text{since $c$ is a distribution})\nn\\
&\leq||\Phi r'-J^*||_\infty+||J^*-\hv||_\infty\,. & (\text{triangle inequality}) \label{mt2eq0}
\end{align}
Now, by another triangle inequality,
\begin{align}
||\Phi r'-J^*||_\infty&\leq ||\Phi r^* -J^*||_\infty+||\Phi r'-\Phi r^*||_\infty
\leq \gamma+\frac{(1+\alpha)\gamma}{1-\alpha}=\frac{2\gamma}{1-\alpha}.
\label{mt2eq1}
\end{align}
The result follows by combining this bound with \eqref{mt2eq0} and \cref{cmt1}.
\end{proof}

\begin{corollary}[Prediction error bound]
\label{cmt2}
%Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2}, then \todoc{Where is the effect of $\chi$?}
We have
\begin{align}\label{finalbnd}
||J^*-\hj||_{1,c}\leq\frac{6 ||J^*-\Phi r^*||_\infty+2||\Gamma J^*-\hg J^*||_\infty}{1-\alpha}\,.
\end{align}
\end{corollary}
\begin{proof}
We have
$
||J^*-\hj||_{1,c}\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}
\leq||J^*-\hv||_\infty+||\hv-\hj||_{1,c}
$.
The result now follows from \cref{cmt1} and \cref{mt2}.
\end{proof}
When no constraints are removed, $\Gamma = \hg$. In this case, \eqref{finalbnd} can be compared to the bound in \cref{restateval} instantiated with $\psi = \one$, in which case the right-hand side of \eqref{finalbnd}
becomes $\frac{2\norm{J^* - \Phi r^*}_{\infty}}{1-\alpha}$, i.e., the bound  \eqref{finalbnd} is a off by a factor three 
only from that in \cref{restateval}.
We view this as a small price paid to be paid for the increased generality of \eqref{finalbnd}.
In terms of the price of removing constraints,
the result shows that there is effectively no price to be paid for removing constraints as long as
those constraints that are binding in the definition of $\Gamma J^*(i)$, $1\le i \le n$ are kept: 
a rather intuitive result.
\todoc{I am still trying to understand whether it is good or bad that the result is independent of $\N$.
}

Just like in the case of RLPs, it is possible to tighten the bounds by using weighted $\max$-norms. 
This is the subject of the next section.
